\plaintitle

### 2016-09-19 drafts/labor/relationships.tex
abstract and title closed out
intro notes resolved, some requests for feedback i also changed it so that \ali and \msb notes don't show up in the final document, but do show up in the constituent parts. if you want to undo that, comment lines 124-127 (or just 126-127)
pushing whatever i have...

\subsubsection[the relationships of workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
\item with \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
\topic{A number of ethical questions surrounding the
increasing complexity of crowd work have arisen in recent years.}
\citeauthor{professionalcrowdworkEthics} bring some of these issues to light
--- working for increasing amounts of time on tasks of growing complexity%
, only to discover that requesters are not willing to pay%
, for instance ---
but these and other dangers range an enormous landscape
\cite{professionalcrowdworkEthics}.
\citeauthor{crowdworkFuture}
list a few of the problems they identified in \citeyear{crowdworkFuture}
--- motivation, feedback, reputation, quality control, to name a few ---
while others discuss challenges such as fostering collective action
and the opportunity for learning and career advancement
\cite{crowdworkFuture,nickerson2013crowd,dynamo}.

>>>>

\subsubsection[What will work and the place of work look like for workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
\item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\ali{

\subsubsubsection{\crowdworkpers}
\begin{enumerate}
  \item with work: what is this to workers? is it social, as \citeauthor{Jung:2016:SFG:2851581.2892328} says?
        it seems like no according to \citeauthor{fort2011amazon}.
        a few have tried to understand this from a turker's view
        (see \citeauthor{martin2014being} and bigham's blog post);
        generally trying to understand why people would do this work (\citeauthor{whyWouldAnyoneBrewer})
        \cite{whyWouldAnyoneBrewer,Jung:2016:SFG:2851581.2892328,
              martin2014being,fort2011amazon}.
  \item with requesters: most of what we know about crowd workers as they relate to requesters, or employers,
        comes from our recognition of the frustration workers have;
        \citeauthor{fixingChaos} talks about the chaos of turking and the unilateral power requesters have;
        \citeauthor{turkopticon} highlight the information asymmetry between workers and requesters on AMT.
        \citeauthor{dynamo} point out the frustration workers experience trying
        to communicate collectively with requesters.
        some research frames this tension as the turker's problem
        (see \citeauthor{MaliciousCrowdworkersGadiraju}),
        but some has taken a more even--handed view (\citeauthor{takingAHITMcInnis})
        \cite{turkopticon,dynamo,MaliciousCrowdworkersGadiraju,takingAHITMcInnis}.
  \item with other workers: \citeauthor{dynamo} specifically points out the ``mega--drama'' among workers;
        \citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
        the culture of crowd work and the study thereof.
        \citeauthor{crowdcollab} quantifies and maps this social network of turkers
        (this is different from the requesters topic because
        researchers like Irani, Gray, etc\dots~aren't Turkers, but are as close to
        ``cultural anthropologists doing ethnography'' as we see on AMT, maybe online in general)
        \cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab}.
\end{enumerate}

\subsubsubsection{\pieceworkpers}
\begin{enumerate}
  \item with work: how do workers relate to work?
        \citeauthor{riisOtherSideLives} documents this to some extent,
        but doesn't say that much about interviews or anything like that.
        a handful of sources suggest to know something about
        how workers relate to the work, like \citeauthor{clark1908cotton},
        but this distinctly doesn't bring the worker's perspective into the discussion;
        it projects an etic view, rather than attempts to understand from an emic view.
        then again, this was a time before Boas and Malinowski, so maybe this is natural.
        \cite{riisOtherSideLives,clark1908cotton}.
  \item with requesters:
        \cite{levi2009union,ahlquist2013interest,
              mccallum2013global,jacoby1983union}?
  \item with other workers: this is harder; crowd work research doesn't just benefit from
        digitally mediated technology allowing us to make
        relationship networks like \citeauthor{crowdcollab} did;
        we also benefit from what we consider modern Anthropology and ethnography,
        something which fundamentally didn't exist or was still in its infancy during piecework's life.
        Still, we can look at primary sources, like \cite{american1921problem} by
        the president of the American Federation of Labor,
        to give us some hint of how they related to each other
        \cite{american1921problem,crowdcollab}
\end{enumerate}

\subsubsubsection{\whatchanged}

}

% \paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
\topic{A number of ethical questions surrounding the
increasing complexity of crowd work have arisen in recent years.}
\citeauthor{professionalcrowdworkEthics} bring some of these issues to light
--- working for increasing amounts of time on tasks of growing complexity%
, only to discover that requesters are not willing to pay%
, for instance ---
but these and other dangers range an enormous landscape
\cite{professionalcrowdworkEthics}.
\citeauthor{crowdworkFuture}
list a few of the problems they identified in \citeyear{crowdworkFuture}
--- motivation, feedback, reputation, quality control, to name a few ---
while others discuss challenges such as fostering collective action
and the opportunity for learning and career advancement
\cite{crowdworkFuture,nickerson2013crowd,dynamo}.
